Parameter Space Representation of Pareto Front to Explore Hardware-Software Dependencies

### 2014-10-28 experiments.tex
added gratis partitioning discussion draft

\figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the resulting Pareto fronts for two
different scenarios of 100 and 500 simulations budget. \comment{AA: per curiosita': quando facevi piu' run, PS andava ancora peggio rispetto a GA?} When possible,
similar algorithm parameters have been adopted. In particular a
population size of 30 has been chosen for the genetic approach (GA), corresponding to the
same value for the $K$ of PS. \comment{AA: che valore di $alpha$ hai usato?} The number of generations (or era)
has been chosen so that the only the given amount of simulations is
actually performed. Thus, when accounting these simulations only unique simulations
has been considered, removing repetitions and unfeasible
configurations.

@@

Low budget Pareto sets are shown in \figR{pareto_fronts_100}. With a so small number of
configuration being investigated the two sets are often overlapping,
being also strongly dependent upon the application being considered.
These results are obtained in about 5 eras and demonstrate that with a so limited budget PS can compete with
genetic approach while even discovering very different Pareto fronts. 
Considering the extended simulation budget as depicted in
\figR{pareto_fronts_500}, we can qualitatively observe that
even if PS does not strictly outperforms genetic in terms of dominance, it shows in
some cases largely Pareto in terms of extension. We can intuitively
relate this to the ``novelty-based'' score system, so that instead of
focusing on getting better points inside a given range it tries to
enlarge the range itself, resulting in less dense but more extended
Paretos. Of course we cannot classify this different behaviour as
``better'' or ``worse'' as compared to the genetic one, it depends on
various design factors such as desired results granularity, prefixed objective
range constraints, estimated error of the models used etc.

@@

\figR{dispersion}(c) shows the average normalised absolute
dispersion errors for different benchmarks for PS and GA
exploration. As it can be observed, GA shows a tendency in
discovering more uniformly dispersed points (i.e. higher values in the
chart). These results,
together with the variation ranges of \figR{dispersion}(a) and
(b) confirm the of density vs extension trade-offs
when comparing PS and GA approaches. Again, it
is worth pointing out how a definitive claim about the superiority of
the PS behaviour is strictly dependent on the design 
requirements and constraints, e.g. whether we need wide or dense
results. Nevertheless, the proposed algorithm introduces a new
perspective on the allocation of a simulations budget, paving the way for
the development of further strategies for addressing the problem of
multi-objective hardware/software design space exploration.

>>>>

\figR{pareto_fronts_100} and \figR{pareto_fronts_500} show the
resulting Pareto fronts for two different scenarios of 100 and 500
simulations budget. The set of algorithm parameters involved and their
values are the one previously shown in Table~\ref{tab:defaults}. It
should be pointed out again that the number of generations (or era)
has been chosen so that only the given amount of simulations is
actually performed. Thus, when accounting these simulations only
unique simulations has been considered, removing repetitions and
unfeasible configurations.

@@

Low budget Pareto sets are shown in \figR{pareto_fronts_100}. Note
that with a so small number of configuration being investigated the
two sets are often overlapping, being also strongly dependent upon the
application being considered.  These results are obtained in about 5
eras and demonstrate that with a so limited budget PS can compete with
genetic approach while even discovering very different Pareto fronts.
Considering the extended simulation budget as depicted in
\figR{pareto_fronts_500}, we can qualitatively observe that even if PS
does not strictly outperforms genetic in terms of dominance, it shows
in some cases largely Pareto in terms of extension. We can intuitively
relate this to the ``novelty-based'' score system, so that instead of
focusing on getting better points inside a given range it tries to
enlarge the range itself, resulting in less dense but more extended
Paretos. Of course we cannot classify this different behaviour as
``better'' or ``worse'' as compared to the genetic one, it depends on
various design factors such as desired results granularity, prefixed
objective range constraints, estimated error of the models used etc.

@@

\figR{dispersion}(c) shows the average normalised absolute
dispersion errors for different benchmarks for PS and GA
exploration. As it can be observed, GA shows a tendency in
discovering more uniformly dispersed points (i.e. higher values in the
chart). These results, together with the variation ranges of \figR{dispersion}(a) and
(b) confirm the of density vs extension trade-offs
when comparing PS and GA approaches. Again, it
is worth pointing out how a definitive claim about the superiority of
the PS behaviour is strictly dependent on the design 
requirements and constraints, e.g. whether we need wide or dense
results.

\comments{Da lasciare, da spostare ? da mostrare in modo semplice ?
non so}
Another interesting feature of PS is that the final output of its
execution is not only the set of pareto optimal configurations, but also a set
of more or less innovation regions of the parameter space, obtained as
a result of the merge/splitting operators described
in~\secR{algorithm}.

%Nevertheless, the proposed algorithm introduces a new
%perspective on the allocation of a simulations budget, paving the way for
%the development of further strategies for addressing the problem of
%multi-objective hardware/software design space exploration.
